Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-02-23 paper/main.tex
Addressed a few more of the referee's points

\begin{deluxetable}{cccc}
\tabletypesize{\scriptsize}
\tablewidth{0pt}
\tablecaption{MWA Observations of PSR \psr{} \label{tab:observations}}
\tablehead{
\colhead{MJD} & \colhead{Obs ID} & \multicolumn{2}{c}{Number of rotations} \\
& & Total & With detectable emission
}
\startdata
58434 & 1226062160 & 3759 & 788 \\
58991 & 1274143152 & 914  & 358 \\
59003 & 1275178816 & 914  & 281 \\
59094 & 1283104232 & 1374 & 545
\enddata
\tablecomments{All observations are in the $140$-$170\,$MHz band, with $100\,\mu$s/$10\,$kHz resolutions.}
\end{deluxetable}

Each observation was individually calibrated using dedicated calibration observations of nearby bright sources and the Real Time System \citep{Mitchell2008}.
After calibration, the voltages were used to form a tied-array beam in the direction of the pulsar (the localization procedure is discussed in \S\ref{sec:localization}), using the bespoke beamforming software described in \citet{Ord2019}.
After determining the best dispersion measure (DM) and period (see \S\ref{sec:period}), de-dispersion and folding were performed with {\tt DSPSR} \citep{VanStraten2011b} and {\tt PSRCHIVE} \citep{Hotan2004} to form single pulse archives, from which Stokes I pulse stacks were created.
Profiles of each detection, as well as an integrated profile incorporating the data from all four observations, is shown in Fig \ref{fig:profiles}.
Subsequent analysis of the pulse stacks is described in \S\ref{sec:analysis}.
\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{profiles.png}
    \caption{Mean profiles of the four observations with detections, and the total mean profile (top panel) including all four observations, with a time resolution of $\sim 1.3\,$ms. The profiles show a barely resolved double peak structure.}
    \label{fig:profiles}
\end{figure}

>>>>

\begin{deluxetable}{ccccc}
\tabletypesize{\scriptsize}
\tablewidth{0pt}
\tablecaption{MWA Observations of PSR \psr{} \label{tab:observations}}
\tablehead{
\colhead{MJD} & \colhead{Obs ID} & \multicolumn{2}{c}{Number of rotations} \\
& & Total & With detectable emission
}
\startdata
58434 & 1226062160 & 3759 & 788 \\
58991 & 1274143152 & 914  & 358 \\
59003 & 1275178816 & 914  & 281 \\
59094 & 1283104232 & 1374 & 545
\enddata
\tablecomments{All observations are in the $140$-$170\,$MHz band, with $100\,\mu$s/$10\,$kHz resolutions.}
\end{deluxetable}

Each observation was individually calibrated using {\bf observations of 3C444 taken within $\sim 2$ hours of the respective target observations.
The calibration solutions were obtained using} the Real Time System software \citep{Mitchell2008}.
After calibration, the voltages were used to form a tied-array beam in the direction of the pulsar (the localization procedure is discussed in \S\ref{sec:localization}), using the bespoke beamforming software described in \citet{Ord2019}.
{\bf The MWA is located in a very radio quiet location, and no significant RFI was found in the beamformed data.}
After determining the best dispersion measure (DM) and period (see \S\ref{sec:period}), de-dispersion and folding were performed with {\tt DSPSR} \citep{VanStraten2011b} and {\tt PSRCHIVE} \citep{Hotan2004} to form single pulse archives, from which Stokes I pulse stacks were created.
Profiles of each detection, as well as an integrated profile incorporating the data from all four observations, is shown in Fig \ref{fig:profiles}.
Subsequent analysis of the pulse stacks is described in \S\ref{sec:analysis}.
\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{profiles.png}
    \caption{{\bf Peak-normalised} mean profiles of the four observations with detections, and the total mean profile (top panel) including all four observations, with a time resolution of $\sim 1.3\,$ms. The profiles show a barely resolved double peak structure.}
    \label{fig:profiles}
\end{figure}
